Enhancement of SDR in Thessaloniki

### 2024-04-23 GHI_enh_Aeronet.tex
Commit 2024-04-23 19:30

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-22}

@@

@@

@@

\begin{verbatim}
2024-04-22 07:36:33.0 athan@tyler GHI_enh_Aeronet.R 0.673847 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-23}

@@

\begin{verbatim}
[1] "Month Exact" "SZA min"     "SZA mean"    "SZA median" 
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_Aeronet_files/figure-latex/unnamed-chunk-4-9} \end{center}

@@

\begin{verbatim}
2024-04-23 15:57:24.4 athan@tyler GHI_enh_Aeronet.R 0.931960 mins
\end{verbatim}
